# Geoms and Statistics

Geometric objects (geoms) define the basic shape of the elements on the plot. 

- Every geom has a default statistic
- Every statistic has a default geom

You can get a list of all geoms using the online help in RStudio

```{r}
help.search("geom_", package = "ggplot2")
```

Change the size of each bin:

```{r}
ggplot(housing, aes(x = Home.Value)) +
  geom_histogram(binwidth = 1000)
```

Add a mapping for the fill color:

```{r}
ggplot(housing, aes(x = Home.Value, fill = Region)) +
  geom_histogram(binwidth = 1000)
```

Mapping can also be specified in the geom:

```{r}
ggplot(housing, aes(x = Home.Value)) +
  geom_histogram(aes(fill = Region), binwidth = 1000)
```


Same plot can also be created using `stat_bin` transformation. The default geom for stat_bin is "area"

```{r}
ggplot(housing, aes(x = Home.Value)) +
  stat_bin(binwidth = 1000)
```

Change the default geom to `"point"`

```{r}
ggplot(housing, aes(x = Home.Value)) +
  stat_bin(geom = "point", binwidth = 1000)
```

Change the default geom to `"line"`

```{r}
ggplot(housing, aes(x = Home.Value)) +
  stat_bin(geom = "line", binwidth = 1000)
```

## Exercise

Create a subset of housing data from New York since 2000

```{r}
newyork2k <- subset(newyork, Year >= 2000)
```

1. Create a plot that includes multiple geometric objects, for example, lines and points.

    ```{r echo = FALSE}
    ggplot(newyork2k, aes(x = Date, y = Home.Value)) +
      geom_line() +
      geom_point()
    ```

1. Change the shape to be hollow diamond

    HINT: Take a look at **Shape Scales** in the [Data Visualization with ggplot2 Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf)

    ```{r echo = FALSE}
    ggplot(newyork2k, aes(x = Date, y = Home.Value)) +
      geom_point(shape = 5)
    ```

1. Change the size of the point based on `Land.Value` and color based on `Structure.Cost`

    ```{r echo = FALSE}
    ggplot(newyork2k, aes(x = Date, y = Home.Value)) +
      geom_point(aes(size = Land.Value, color = Structure.Cost))
    ```
