# Getting Started

## Prerequisites

Basic knowledge of working with datasets in R is essential. This course assumes that you're comfortable with reading and manipulating datasets, working with script files, and navigating in RStudio. No prior experience with plotting functions in R is not required.

## Software Requirements

### R and RStudio

Recent versions of R (version 3.2 or newer) and RStudio (version 0.99 or above) are required.

You can download the latest versions from the links below:

- [Download R](https://cran.r-project.org)
- [Download RStudio](https://www.rstudio.com/products/rstudio/download)

You can find out the version of R installed by typing `version` at the console:

```{r}
version
```

## Installing ggplot2

If you don't have ggplot2 installed, you can install it using the `install.packages()` function:

```{r eval = FALSE}
install.packages("ggplot2")
```

You can find out the version of ggplot installed using the `packageVersion()` function:

```{r}
packageVersion("ggplot2")
```

## Installing ggplot2 Extentions

We need the following ggplot extensions for this tutorial:

```{r eval = FALSE}
install.packages("scales")
install.packages("ggrepel")
install.packages("ggthemes")
```

