# Scales

Let's create another subset that includes only the data from the first quarter of 2001.

```{r}
housing2001q1 <- subset(housing, Year == 2001 & Quarter == 1)
```

And now we create a scatter plot with this dataset

```{r}
ggplot(housing2001q1, aes(x = Land.Value, y = Structure.Cost)) + 
  geom_point()
```

Our dataset is skewed so in order to help with interpretation, let's change the x-axis to log scale

```{r}
ggplot(housing2001q1, aes(x = Land.Value, y = Structure.Cost)) + 
  geom_point() + 
  scale_x_log10()
```

Now add a dollar sign in front of our axis labels

```{r}
ggplot(housing2001q1, aes(x = Land.Value, y = Structure.Cost)) + 
  geom_point() + 
  scale_x_log10(labels = dollar) +
  scale_y_continuous(labels = dollar)
```

Next we change the scale for the x-axis which is in a Date format and control the breaks for y-axis which is a continuous variable.

```{r}
ggplot(northeast, aes(x = Date, y = Home.Value, color = State)) +
  geom_line() +
  scale_x_date(date_breaks ="3 year", date_minor_breaks ="1 year", date_labels = "'%y") +
  scale_y_continuous(breaks = seq(0, 500000, 50000), labels = dollar) 
```


